Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-10 SupportingInformation.Rmd
fixing tables

 #atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$",
 #                               "$\\Ps_{0,0.1}-\\Ps_{0.9,1}$",
 #                               "$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
 atdres<-data.frame(Statistic=c("$\\cor_\\text{first slice}-\\cor_\\text{last slice}$",
                               "$\\Ps_\\text{first slice}-\\Ps_\\text{last slice}$",
                                "$\\Dsq_\\text{last slice}-\\Dsq_\\text{first slice}$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)

@@

```{r tab_soilCN_asym,echo=F,results="markup"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_soilCN_asym<-make_table_stat_fn(data=stat_soilCN_ga)
tab_soilCN_asym[,1]<-c("corFS-corLS","PFS-PLS","D2LS-D2FS")
knitr::kable(tab_soilCN_asym, booktabs = T, 
             format = "latex",linesep = "",
      caption.short = "Nonparametric asymmetry tests against an N-copula null, soil C and N",
      caption = "Soil C and N dataset results for nonparametric tests of whether asymmetry of tail dependence was significant, compared to an N-copula null hypothesis. The values of the listed statistics (corFS-corLS $=\\cor_{0,0.1}-\\cor_{0.9,1}$, PFS-PLS $=\\Ps_{0,0.1}-\\Ps_{0.9,1}$, D2LS-D2FS $=\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$; here FS stands for `first slice' and LS for `last slice') for real data were compared to their values for 1000 Kendall- or Spearman-preserving N surrogates, in seperate comparisons. A table entry $<X$ indicates the value of the given statistic on the data was less than its value on $X$ of the surrogates, so entries of the form $<X$ for $X$ equal to $975$ or above indicate that upper-tail dependence was significantly stronger than lower-tail dependence.\\label{tab_soilCN_asym}")
#kable_styling(, position = "float_left")
```

@@

```{r tab_bmr_birds_asym, echo=F, results="markup"}
tab_bmr_birds_asym<-make_table_stat_fn(data=stat_birds_ga)
tab_bmr_birds_asym[,1]<-c("corFS-corLS","PFS-PLS","D2LS-D2FS")
knitr::kable(tab_bmr_birds_asym,
             format="latex",linesep = "",
             caption.short = "Nonparametric asymmetry tests against an N-copula null, bird body mass and BMR",
             caption = "Bird body mass and BMR dataset results for nonparametric tests of whether asymmetry of tail dependence was significant, compared to an N-copula null hypothesis. Same format as Table \\ref{tab_soilCN_asym}, see caption of that figure.\\label{tab_bmr_birds_asym}",
             booktabs=T)
```

@@

```{r tab_bmr_mammals_asym, echo=F, results="markup"}
tab_bmr_mammals_asym<-make_table_stat_fn(data=stat_mammals_ga)
tab_bmr_mammals_asym[,1]<-c("corFS-corLS","PFS-PLS","D2LS-D2FS")
knitr::kable(tab_bmr_mammals_asym,
             format="latex",linesep = "",
             caption.short = "Nonparametric asymmetry tests against an N-copula null, mammal body mass and BMR",
             caption = "Mammal body mass and BMR dataset results for nonparametric tests of whether asymmetry of tail dependence was significant, compared to an N-copula null hypothesis. Same format as Table \\ref{tab_soilCN_asym}, see caption of that figure. \\label{tab_bmr_mammals_asym}",
             booktabs=T)
```

@@

```{r tab_cc_asym_2000, echo=F, results="markup"}
tab_cc_asym_2000<-make_table_stat_fn(data=stat_cc_ga$`2000`)
tab_cc_asym_2000[,1]<-c("corFS-corLS","PFS-PLS","D2LS-D2FS")
knitr::kable(tab_cc_asym_2000,
             format="latex",linesep = "",
             caption.short = "Nonparametric asymmetry tests against an N-copula null, Cedar Creek data",
             caption = "Cedar Creek dataset results for nonparametric tests of whether asymmetry of tail dependence was significant, compared to an N-copula null hypothesis. Same format as Table \\ref{tab_soilCN_asym}, see caption of that figure.\\label{tab_cc_asym_2000}",
             booktabs=T)
```

@@

```{r tab_count_AICw, echo=F, results='markup'}
knitr::kable(round(RES_aphid_count$info_ord_AICw[,,1],3), 
             format='latex',linesep = "",
             caption.short = "AIC weights, best-fitting copulas, green spruce aphid abundance data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for green spruce aphid abundance data.\\label{tab_count_AICw}",
             booktabs=TRUE
             )
```

```{r tab_count_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(round(normal_cop_AICw_matrix(r=RES_aphid_count),3),
             format='latex',linesep = "",
             caption.short = "AIC weights, N copulas, green spruce aphid abundance data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the N copula family for each location pair for green spruce aphid abundance data, for comparison with Table \\ref{tab_count_AICw}. \\label{tab_count_AICw_normal}",
             booktabs=TRUE
             )
```

```{r tab_count_p_CvM, echo=F, results='markup'}
knitr::kable(round(RES_aphid_count$gfc_p_CvM,3),
             format='latex',linesep = "",
             caption.short="Goodness of fit of best-fitting copulas, green spruce aphid abundance data",
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for green spruce abundance data.\\label{tab_count_p_CvM}",
             booktabs=TRUE
             )
```

```{r tab_count_p_KS, echo=F, results='markup'}
knitr::kable(round(RES_aphid_count$gfc_p_KS,3),
             format='latex',linesep = "",
             caption.short="Goodness of fit of best-fitting copulas, green spruce aphid abundance data",
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for green spruce abundance data.\\label{tab_count_p_KS}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_count_LTdep_AICw, echo=F, results='markup'}
knitr::kable(round(RES_aphid_count$LTdep_AICw,3),
             format='latex',linesep = "",
             caption.short="Lower-tail dependence, green spruce aphid abundance data",
             caption = "Model-averaged lower-tail dependence statistics for each location pair for green spruce aphid abundance data.\\label{tab_count_LTdep_AICw}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_count_UTdep_AICw, echo=F, results='markup'}
knitr::kable(round(RES_aphid_count$UTdep_AICw,3),
             format='latex',linesep = "",
             caption.short="Upper-tail dependence, green spruce aphid abundance data",
             caption = "Model-averaged upper-tail dependence statistics for each location pair for green spruce aphid abundance data.\\label{tab_count_UTdep_AICw}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_count_LTmUT, echo=F, results='markup'}
knitr::kable(round(RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw,3),
             digits = 5,linesep = "",
             format='latex',
             caption.short="Lower- minus upper-tail dependence, green spruce aphid abundance data",
             caption = "Model-averaged lower-tail dependence statistics minus model-averaged upper-tail dependence statistics for each location pair for green spruce aphid abundance data.\\label{tab_count_LTmUT}",
             booktabs=TRUE
             )
```

@@

<!--Show the statistical results in a table-->
```{r tab_count_resamp,echo=F,results="markup"}
s<-stat_aphid_count$numericdf[,c(3,2,4)]
sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
colnames(s)<-c("","2.5th quantile", "Mean", "97.5th quantile")
knitr::kable(s,
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, green spruce aphid abundance data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for green spruce aphid abundance data.\\label{tab_count_resamp}",
             booktabs=TRUE)
```

@@

```{r tab_ff_AICw, echo=F, results='markup'}
knitr::kable(round(RES_aphid_ff$info_ord_AICw[,,1],3), 
             format='latex',linesep = "",
             caption.short="AIC weights, best-fitting copulas, leaf-curling plum aphid first flight data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for leaf-curling plum aphid first flight data.\\label{tab_ff_AICw}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_ff_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(round(normal_cop_AICw_matrix(r=RES_aphid_ff),3),
             format='latex',linesep = "",
             caption.short="AIC weights, N copulas, leaf-curling plum aphid first flight data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for leaf-curlung plum aphid first flight data, for comparison with Table \\ref{tab_ff_AICw}.\\label{tab_ff_AICw_normal}",
             booktabs=TRUE
             )
```

```{r tab_ff_p_CvM, echo=F, results='markup'}
knitr::kable(round(RES_aphid_ff$gfc_p_CvM,3),
             format='latex',linesep = "",
             caption.short="Goodness of fit of best-fitting copulas, leaf-curling plum aphid first flight data",
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for leaf-curling plum aphid first flight data.\\label{tab_ff_p_CvM}",
             booktabs=TRUE
             )
```

```{r tab_ff_p_KS, echo=F, results='markup'}
knitr::kable(round(RES_aphid_ff$gfc_p_KS,3),
             format='latex',linesep = "",
             caption.short="Goodness of fit of best-fitting copulas, leaf-curling plum aphid first flight data",
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for leaf-curling plum aphid first flight data.\\label{tab_ff_p_KS}",
             booktabs=TRUE
             )
```

```{r tab_ff_LTdep_AICw, echo=F, results='markup'}
knitr::kable(round(RES_aphid_ff$LTdep_AICw,3),
             format='latex',linesep = "",
             caption.short="Lower-tail dependence, leaf-curling plum aphid first flight data",
             caption = "Model-averaged lower-tail dependence statistics for each location pair for leaf-curling plum aphid first flight data.\\label{tab_ff_LTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_ff_UTdep_AICw, echo=F, results='markup'}
knitr::kable(round(RES_aphid_ff$UTdep_AICw,3),
             format='latex',linesep = "",
             caption.short="Upper-tail dependence, leaf-curling plum aphid first flight data",
             caption = "Model-averaged upper-tail dependence statistics for each location pair for leaf-curling plum aphid first flight data.\\label{tab_ff_UTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_ff_LTmUT, echo=F, results='markup'}
knitr::kable(round(RES_aphid_ff$LTdep_AICw-RES_aphid_ff$UTdep_AICw,3),
             digits = 5,
             format='latex',linesep = "",
             caption.short="Lower- minus upper-tail dependence, leaf-curling plum aphid first flight data",
             caption = "Model-averaged lower-tail dependence statistics minus model-averaged upper-tail dependence statistics for each location pair for leaf-curling plum aphid first flight data.\\label{tab_ff_LTmUT}",
             booktabs=TRUE
             )
```

@@

<!--display the main statistical results in a table-->
```{r tab_ff_resamp,echo=F,results="markup"}
s<-stat_aphid_ff$numericdf[,c(3,2,4)]
sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
colnames(s)<-c("","2.5th quantile", "Mean", "97.5th quantile")
knitr::kable(s,
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, leaf-curling plum aphid first flight data",
             caption = "Average values of statistics across all location pairs and confidence intervals based on spatial resampling for leaf-curling plum aphid first flight data.\\label{tab_ff_resamp}",
             booktabs=TRUE)
```

@@

```{r tab_pns_AICw,echo=F,results="markup"}
h<-RES_plankton_north_sea$info_ord_AICw[,,1]
h[is.infinite(h)]<-NA
knitr::kable(round(h,3),
             format="latex",
             digits=3,linesep = "",
             caption.short="AIC weights, best-fitting copulas, \\textit{Ceratium furca} abundance data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for \\textit{Ceratium furca} abundance data.\\label{tab_pns_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_AICw_normal,echo=F,results="markup"}
source("normal_cop_AICw.R")
h<-normal_cop_AICw_matrix(r=RES_plankton_north_sea)
h[is.infinite(h)]<-NA
knitr::kable(round(h,3),
             format="latex",linesep = "",
             digits=3,
             caption.short="AIC weights, N copulas, \\textit{Ceratium furca} abundance data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the N copula family for each location pair for \\textit{Ceratium furca} abundance data, for comparison with Table \\ref{tab_pns_AICw}.\\label{tab_pns_AICw_normal}",
             booktabs=TRUE)
```

```{r tab_pns_p_CvM,echo=F,results="markup"}
h<-RES_plankton_north_sea$gfc_p_CvM
h[is.infinite(h)]<-NA
knitr::kable(round(h,3),
             format="latex",linesep = "",
             digits=3,
             caption.short="Goodness of fit of best-fitting copulas, \\textit{Ceratium furca} abundance data",
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for \\textit{Ceratium furca} abundance data.\\label{tab_pns_p_CvM}",
             booktabs=TRUE)
```

```{r tab_pns_p_KS,echo=F,results="markup"}
h<-RES_plankton_north_sea$gfc_p_KS
h[is.infinite(h)]<-NA
knitr::kable(round(h,3),
             format="latex",linesep = "",
             digits=3,
             caption.short="Goodness of fit of best-fitting copulas, \\textit{Ceratium furca} abundance data",
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of
the goodness of fit of the lowest-AIC copula family for each pair of
locations for \\textit{Ceratium furca} abundance data.\\label{tab_pns_p_KS}",
             booktabs=TRUE)
```

```{r tab_pns_LTdep_AICw,echo=F,results="markup"}
h<-RES_plankton_north_sea$LTdep_AICw
h[is.infinite(h)]<-NA
knitr::kable(round(h,3),
             format="latex",linesep = "",
             digits=3,
             caption.short="Lower-tail dependence, \\textit{Ceratium furca} abundance data",
             caption = "Model-averaged lower-tail dependence statistics for each location pair for \\textit{Ceratium furca} abundance data.\\label{tab_pns_LTdep_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_UTdep_AICw,echo=F,results="markup"}
h<-RES_plankton_north_sea$UTdep_AICw
h[is.infinite(h)]<-NA
knitr::kable(round(h,3),
             format="latex",linesep = "",
             digits=3,
             caption.short="Upper-tail dependence, \\textit{Ceratium furca} abundance data",
             caption = "Model-averaged upper-tail dependence statistics for each location pair for \\textit{Ceratium furca} abundance data.\\label{tab_pns_UTdep_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_LTmUT,echo=F,results="markup"}
h<-RES_plankton_north_sea$LTdep_AICw-RES_plankton_north_sea$UTdep_AICw
h[is.nan(h)]<-NA
knitr::kable(round(h,3),
             format="latex",linesep = "",
             digits=3,
             caption.short="Lower- minus upper-tail dependence, \\textit{Ceratium furca} abundance data",
             caption = "Model-averaged lower-tail dependence statistics minus model-averaged upper-tail dependence statistics for each location pair for \\textit{Ceratium furca} abundance data.\\label{tab_pns_LTmUT}",
             booktabs=TRUE)
```

@@

```{r tab_methane_AICw,echo=F,results="markup"}
h<-RES_methane$info_ord_AICw[,,1]
h[is.infinite(h)]<-NA
knitr::kable(round(h,3),
             format="latex",linesep = "",
             digits=3,
             caption.short="AIC weights, best-fitting copulas, methane flux data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for methane flux data.\\label{tab_methane_AICw}",
             booktabs=TRUE)
```

>>>>

 #atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$",
 #                               "$\\Ps_{0,0.1}-\\Ps_{0.9,1}$",
 #                               "$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
 atdres<-data.frame(Statistic=c("cor$_{FS}$-cor$_{LS}$",
                               "P$_{FS}$-P$_{LS}$",
                                "D$_{LS}^2$-D$_{FS}^2$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)

@@

```{r tab_soilCN_asym,echo=F,results="markup"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_soilCN_asym<-make_table_stat_fn(data=stat_soilCN_ga)
#tab_soilCN_asym[,1]<-c("corFS-corLS","PFS-PLS","D2LS-D2FS")
knitr::kable(tab_soilCN_asym, booktabs = T, escape=F,
             format = "latex",linesep = "",
      caption.short = "Nonparametric asymmetry tests against an N-copula null, soil C and N",
      caption = "Soil C and N dataset results for nonparametric tests of whether asymmetry of tail dependence was significant, compared to an N-copula null hypothesis. The values of the listed statistics (cor$_{FS}$-cor$_{LS}$ = $\\cor_{0,0.1}-\\cor_{0.9,1}$, P$_{FS}$-P$_{LS}$ = $\\Ps_{0,0.1}-\\Ps_{0.9,1}$, D$_{LS}^2$-D$_{FS}^2$ = $\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$; here FS stands for `first slice' and LS for `last slice') for real data were compared to their values for 1000 Kendall- or Spearman-preserving N surrogates, in seperate comparisons. A table entry $<X$ indicates the value of the given statistic on the data was less than its value on $X$ of the surrogates, so entries of the form $<X$ for $X$ equal to $975$ or above indicate that upper-tail dependence was significantly stronger than lower-tail dependence.\\label{tab_soilCN_asym}")
```

@@

```{r tab_bmr_birds_asym, echo=F, results="markup"}
tab_bmr_birds_asym<-make_table_stat_fn(data=stat_birds_ga)
#tab_bmr_birds_asym[,1]<-c("corFS-corLS","PFS-PLS","D2LS-D2FS")
knitr::kable(tab_bmr_birds_asym,
             format="latex",linesep = "",escape=F,
             caption.short = "Nonparametric asymmetry tests against an N-copula null, bird body mass and BMR",
             caption = "Bird body mass and BMR dataset results for nonparametric tests of whether asymmetry of tail dependence was significant, compared to an N-copula null hypothesis. Same format as Table \\ref{tab_soilCN_asym}, see caption of that figure.\\label{tab_bmr_birds_asym}",
             booktabs=T)
```

@@

```{r tab_bmr_mammals_asym, echo=F, results="markup"}
tab_bmr_mammals_asym<-make_table_stat_fn(data=stat_mammals_ga)
#tab_bmr_mammals_asym[,1]<-c("corFS-corLS","PFS-PLS","D2LS-D2FS")
knitr::kable(tab_bmr_mammals_asym,
             format="latex",linesep = "",escape=F,
             caption.short = "Nonparametric asymmetry tests against an N-copula null, mammal body mass and BMR",
             caption = "Mammal body mass and BMR dataset results for nonparametric tests of whether asymmetry of tail dependence was significant, compared to an N-copula null hypothesis. Same format as Table \\ref{tab_soilCN_asym}, see caption of that figure. \\label{tab_bmr_mammals_asym}",
             booktabs=T)
```

@@

```{r tab_cc_asym_2000, echo=F, results="markup"}
tab_cc_asym_2000<-make_table_stat_fn(data=stat_cc_ga$`2000`)
#tab_cc_asym_2000[,1]<-c("corFS-corLS","PFS-PLS","D2LS-D2FS")
knitr::kable(tab_cc_asym_2000,
             format="latex",linesep = "",escape=F,
             caption.short = "Nonparametric asymmetry tests against an N-copula null, Cedar Creek data",
             caption = "Cedar Creek dataset results for nonparametric tests of whether asymmetry of tail dependence was significant, compared to an N-copula null hypothesis. Same format as Table \\ref{tab_soilCN_asym}, see caption of that figure.\\label{tab_cc_asym_2000}",
             booktabs=T)
```

@@

```{r tab_count_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$info_ord_AICw[,,1], 
             format='latex',linesep = "",digits=3,
             caption.short = "AIC weights, best-fitting copulas, green spruce aphid abundance data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for green spruce aphid abundance data.\\label{tab_count_AICw}",
             booktabs=TRUE
             )
```

```{r tab_count_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_count),
             format='latex',linesep = "",digits=3,
             caption.short = "AIC weights, N copulas, green spruce aphid abundance data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the N copula family for each location pair for green spruce aphid abundance data, for comparison with Table \\ref{tab_count_AICw}. \\label{tab_count_AICw_normal}",
             booktabs=TRUE
             )
```

```{r tab_count_p_CvM, echo=F, results='markup'}
knitr::kable(RES_aphid_count$gfc_p_CvM,
             format='latex',linesep = "",digits=3,
             caption.short="Goodness of fit of best-fitting copulas, green spruce aphid abundance data",
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for green spruce abundance data.\\label{tab_count_p_CvM}",
             booktabs=TRUE
             )
```

```{r tab_count_p_KS, echo=F, results='markup'}
knitr::kable(RES_aphid_count$gfc_p_KS,
             format='latex',linesep = "",digits=3,
             caption.short="Goodness of fit of best-fitting copulas, green spruce aphid abundance data",
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for green spruce abundance data.\\label{tab_count_p_KS}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_count_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw,
             format='latex',linesep = "",digits=3,
             caption.short="Lower-tail dependence, green spruce aphid abundance data",
             caption = "Model-averaged lower-tail dependence statistics for each location pair for green spruce aphid abundance data.\\label{tab_count_LTdep_AICw}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_count_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$UTdep_AICw,
             format='latex',linesep = "",digits=3,
             caption.short="Upper-tail dependence, green spruce aphid abundance data",
             caption = "Model-averaged upper-tail dependence statistics for each location pair for green spruce aphid abundance data.\\label{tab_count_UTdep_AICw}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_count_LTmUT, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw,
             digits = 3,linesep = "",
             format='latex',
             caption.short="Lower- minus upper-tail dependence, green spruce aphid abundance data",
             caption = "Model-averaged lower-tail dependence statistics minus model-averaged upper-tail dependence statistics for each location pair for green spruce aphid abundance data.\\label{tab_count_LTmUT}",
             booktabs=TRUE
             )
```

@@

<!--Show the statistical results in a table-->
```{r tab_count_resamp,echo=F,results="markup"}
s<-stat_aphid_count$numericdf[,c(3,2,4)]
sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
knitr::kable(s, digits = 3,
             col.names=c("","2.5$^{th}$ quantile", "Mean", "97.5$^{th}$ quantile"),
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, green spruce aphid abundance data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for green spruce aphid abundance data.\\label{tab_count_resamp}",
             booktabs=TRUE)
```

@@

```{r tab_ff_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$info_ord_AICw[,,1], 
             format='latex',linesep = "",digits=3,
             caption.short="AIC weights, best-fitting copulas, leaf-curling plum aphid first flight data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for leaf-curling plum aphid first flight data.\\label{tab_ff_AICw}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_ff_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_ff),
             format='latex',linesep = "",digits=3,
             caption.short="AIC weights, N copulas, leaf-curling plum aphid first flight data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for leaf-curlung plum aphid first flight data, for comparison with Table \\ref{tab_ff_AICw}.\\label{tab_ff_AICw_normal}",
             booktabs=TRUE
             )
```

```{r tab_ff_p_CvM, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$gfc_p_CvM,
             format='latex',linesep = "",digits=3,
             caption.short="Goodness of fit of best-fitting copulas, leaf-curling plum aphid first flight data",
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for leaf-curling plum aphid first flight data.\\label{tab_ff_p_CvM}",
             booktabs=TRUE
             )
```

```{r tab_ff_p_KS, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$gfc_p_KS,
             format='latex',linesep = "",digits=3,
             caption.short="Goodness of fit of best-fitting copulas, leaf-curling plum aphid first flight data",
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for leaf-curling plum aphid first flight data.\\label{tab_ff_p_KS}",
             booktabs=TRUE
             )
```

```{r tab_ff_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$LTdep_AICw,
             format='latex',linesep = "",digits=3,
             caption.short="Lower-tail dependence, leaf-curling plum aphid first flight data",
             caption = "Model-averaged lower-tail dependence statistics for each location pair for leaf-curling plum aphid first flight data.\\label{tab_ff_LTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_ff_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$UTdep_AICw,
             format='latex',linesep = "",digits=3,
             caption.short="Upper-tail dependence, leaf-curling plum aphid first flight data",
             caption = "Model-averaged upper-tail dependence statistics for each location pair for leaf-curling plum aphid first flight data.\\label{tab_ff_UTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_ff_LTmUT, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$LTdep_AICw-RES_aphid_ff$UTdep_AICw,
             digits = 3,
             format='latex',linesep = "",
             caption.short="Lower- minus upper-tail dependence, leaf-curling plum aphid first flight data",
             caption = "Model-averaged lower-tail dependence statistics minus model-averaged upper-tail dependence statistics for each location pair for leaf-curling plum aphid first flight data.\\label{tab_ff_LTmUT}",
             booktabs=TRUE
             )
```

@@

<!--display the main statistical results in a table-->
```{r tab_ff_resamp,echo=F,results="markup"}
s<-stat_aphid_ff$numericdf[,c(3,2,4)]
sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
knitr::kable(s, digits = 3,
             col.names=c("","2.5$^{th}$ quantile", "Mean", "97.5$^{th}$ quantile"),
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, leaf-curling plum aphid first flight data",
             caption = "Average values of statistics across all location pairs and confidence intervals based on spatial resampling for leaf-curling plum aphid first flight data.\\label{tab_ff_resamp}",
             booktabs=TRUE)
```

@@

```{r tab_pns_AICw,echo=F,results="markup"}
h<-RES_plankton_north_sea$info_ord_AICw[,,1]
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",
             digits=3,linesep = "",
             caption.short="AIC weights, best-fitting copulas, \\textit{Ceratium furca} abundance data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for \\textit{Ceratium furca} abundance data.\\label{tab_pns_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_AICw_normal,echo=F,results="markup"}
source("normal_cop_AICw.R")
h<-normal_cop_AICw_matrix(r=RES_plankton_north_sea)
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="AIC weights, N copulas, \\textit{Ceratium furca} abundance data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the N copula family for each location pair for \\textit{Ceratium furca} abundance data, for comparison with Table \\ref{tab_pns_AICw}.\\label{tab_pns_AICw_normal}",
             booktabs=TRUE)
```

```{r tab_pns_p_CvM,echo=F,results="markup"}
h<-RES_plankton_north_sea$gfc_p_CvM
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Goodness of fit of best-fitting copulas, \\textit{Ceratium furca} abundance data",
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for \\textit{Ceratium furca} abundance data.\\label{tab_pns_p_CvM}",
             booktabs=TRUE)
```

```{r tab_pns_p_KS,echo=F,results="markup"}
h<-RES_plankton_north_sea$gfc_p_KS
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Goodness of fit of best-fitting copulas, \\textit{Ceratium furca} abundance data",
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of
the goodness of fit of the lowest-AIC copula family for each pair of
locations for \\textit{Ceratium furca} abundance data.\\label{tab_pns_p_KS}",
             booktabs=TRUE)
```

```{r tab_pns_LTdep_AICw,echo=F,results="markup"}
h<-RES_plankton_north_sea$LTdep_AICw
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Lower-tail dependence, \\textit{Ceratium furca} abundance data",
             caption = "Model-averaged lower-tail dependence statistics for each location pair for \\textit{Ceratium furca} abundance data.\\label{tab_pns_LTdep_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_UTdep_AICw,echo=F,results="markup"}
h<-RES_plankton_north_sea$UTdep_AICw
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Upper-tail dependence, \\textit{Ceratium furca} abundance data",
             caption = "Model-averaged upper-tail dependence statistics for each location pair for \\textit{Ceratium furca} abundance data.\\label{tab_pns_UTdep_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_LTmUT,echo=F,results="markup"}
h<-RES_plankton_north_sea$LTdep_AICw-RES_plankton_north_sea$UTdep_AICw
h[is.nan(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Lower- minus upper-tail dependence, \\textit{Ceratium furca} abundance data",
             caption = "Model-averaged lower-tail dependence statistics minus model-averaged upper-tail dependence statistics for each location pair for \\textit{Ceratium furca} abundance data.\\label{tab_pns_LTmUT}",
             booktabs=TRUE)
```

@@

```{r tab_methane_AICw,echo=F,results="markup"}
h<-RES_methane$info_ord_AICw[,,1]
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="AIC weights, best-fitting copulas, methane flux data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for methane flux data.\\label{tab_methane_AICw}",
             booktabs=TRUE)
```
